### 2020-06-01 writeup/experiments.tex
alg 1

\begin{table}
\begin{minipage}[t]{.58\textwidth}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text
		classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
\end{minipage}
\quad
% \vspace{}
\begin{minipage}[t]{.40\textwidth}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf Standard} & {\bf Alignment} \\
		\midrule
		{\bf MLP}  & > 100\% & 39\% \\
		{\bf LSTM} & 36\% & 36\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
\end{minipage}
\end{table}

@@

{For each task, the goal is to categorize sentiment opinions expressed in the text.
We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}.
}
%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

@@

@@

\textbf{Improving training efficiency via an incremental schedule.}
\todo{}

\textbf{MTL improves labeled data efficiency.}
We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
We further observe that adding the alignment module helps reduce the data efficiency ratio on MLP.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

@@

\begin{figure}[!t]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
		\caption{Task similarity}
		\label{fig_ab_sim}
	\end{subfigure}%
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_sst_trec_lstm.pdf}
		\caption{Data size}
		\label{fig_ab_data}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Covariate shift}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Validating the three takeaways of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
	(c) As source/target data ratio increases, the performance gains from the covariance alignment procedure \cite{WZR20} increase for LSTM and MLP.
	The $y$-axis measures the performance of MTL minus STL.}
	\label{fig_ablation}
\end{figure}

>>>>

\begin{table}
\begin{minipage}[t]{.58\textwidth}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
\end{minipage}
\quad
% \vspace{}
\begin{minipage}[t]{.40\textwidth}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf MTL} & {\bf Alignment} \\
		\midrule
		{\bf MLP}  & 100\% & \textbf{39\%} \\
		{\bf LSTM} & \textbf{36\%} & 36\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
\end{minipage}
\end{table}

@@

{For each task, the goal is to categorize sentiment opinions expressed in the text.
We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM or MLP layer proposed by~\cite{lei2018simple}.
}
%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

@@

\textbf{Baseline.} We compare Algorithm \ref{alg_inc_train} to a model trained with standard multi-task learning approaches.

@@

\textbf{Improving multi-task training efficiency.}
We compare Algorithm \ref{alg_inc_train} to performing multi-task learning.
Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the cost to achieve the same performance on the target task, compared to multi-task learning.

\textbf{Improving transfer learning training efficiency.}
\todo{}

@@

\textbf{Data efficiency.}
We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
We further show that adding the alignment module helps reduce the data efficiency ratio to $36\%$.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

\begin{figure}[!t]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
		\caption{Task similarity}
		\label{fig_ab_sim}
	\end{subfigure}%
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
		\caption{Data size}
		\label{fig_ab_data}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Covariate shift}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Validating the three takeaways of Section \ref{sec_insight} on sentiment analysis tasks. (a) Adding a semantically similar source task in MTL performs better than adding a dissimilar task.
	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer.
	(c) As source/target data ratio increases, the performance gain from the covariance alignment procedure \cite{WZR20} over MTL increases for LSTM and MLP.}
	\label{fig_ablation}
\end{figure}

### 2020-06-01 writeup/transfer.tex
alg 1

\begin{algorithm}[!t]
	\caption{An incremental training schedule for multi-task learning over two tasks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
		\Req Batch size $S$, number of epochs $T$, validation accuracy $\hat{g}(B; W_1, W_2)$.
		\State Divide $(X_1, Y_1)$ randomly into $K$ batches of size $S$ as $(x^{(1)}, y^{(1)}), \dots, (x^{(K)}, y^{(K)})$.
		\For{$i = 1,\dots, K$}
			\For{$j = 1,\dots, T$}
				\State Update $B, W_1, W_2$ using the training data $\set{x^{(j)}, x^{(j)}}_{j=1}^i$ and  $(X_2, Y_2)$.
			\EndFor
		\State Let $a_i = \hat{g}(B; W_1, W_2)$ be the validation accuracy after epoch $i$.
			If $a_i < a_{i-1}$, \textbf{break}.
		\EndFor
	\end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}[!t]
	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
		\Output The trained modules $B, W_2$ optimized for task $2$.
		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
		\For{$i = 1,\dots, S$}
			\For{$j = 1,\dots, T$}
				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
				\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy after epoch $i$.
				\If{$a_i < a_{i-1}$ or $a_i > \tau$}
					\State \textbf{break}
				\EndIf
			\EndFor
		\EndFor
	\end{algorithmic}
\end{algorithm}
